Haskell in Computational Biology

### 2013-05-29 jfp.tex
residue foot note improved

Once a protein alignment is constructed, it~is used to train a
\emph{hidden Markov model}. 
A~hidden Markov model is a probabilistic finite-state machine which 
can assign a probability to any query sequence.
A~protein whose query sequence has a higher probability is more likely to %
be homologous to the proteins in the alignment.
We~write a query sequence as $x_1, \ldots, x_{\scriptscriptstyle N}$,
where each $x_i$~is 
an amino-acid \emph{residue}.\footnote
{In~biology, when an amino acid enters a protein, it often loses a few
atoms, and so within the protein, what's left of the amino acid is called
a \emph{residue}.
In~this paper we use the terms ``amino acid'' and ``residue''
interchangeably.
}
The number of residues, $N$, can differ from the number of columns
in the alignment,~\alignwidth.

>>>>

Once a protein alignment is constructed, it~is used to train a
\emph{hidden Markov model}. 
A~hidden Markov model is a probabilistic finite-state machine which 
can assign a probability to any query sequence.
A~protein whose query sequence has a higher probability is more likely to %
be homologous to the proteins in the alignment.
We~write a query sequence as $x_1, \ldots, x_{\scriptscriptstyle N}$,
where each $x_i$~is 
an amino-acid \emph{residue}.\footnote
{When an amino acid combines with other amino acids to form a protein, it gives up
two hydrogen atoms and an oxygen atom.
What's left is called
a \emph{residue}.
In~this paper we use the terms ``residue'' and ``amino acid'' 
interchangeably.
}
The number of residues, $N$, can differ from the number of columns
in the alignment,~\alignwidth.
